Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-07-20 jsm/speed-presentation/poster/poster.Rmd
fixed minor layout issues

```{r, fig.height = 2.2, fig.width = 6, out.width = '100%'}
latent.config.plot <- ggplot() + 
  geom_point(aes(x = data.matrix[, 1], y = data.matrix[, 2], 
                 colour = factor(z))) + 
  # coord_fixed() + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  labs(x = NULL, y = NULL, colour = NULL, title = 'Latent Vectors') + 
  scale_colour_brewer(palette = 'Set1')

@@

```{r, cache = TRUE, fig.width = 5, fig.height = 2, out.width = '100%'}
n <- 64
Pz <- generate.P.beta(n)
P <- Pz$P
z <- Pz$clustering
X <- embedding(P, 3, 1)
A <- draw.graph(P)
Xhat <- embedding(A, 3, 1)
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)

>>>>

```{r, fig.height = 2.3, fig.width = 6, out.width = '100%'}
latent.config.plot <- ggplot() + 
  geom_point(aes(x = data.matrix[, 1], y = data.matrix[, 2], 
                 colour = factor(z))) + 
  # coord_fixed() + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  labs(x = NULL, y = NULL, colour = NULL, title = 'Latent Vectors') + 
  scale_colour_brewer(palette = 'Set1')

@@

```{r, cache = TRUE, fig.width = 5, fig.height = 2.05, out.width = '100%'}
n <- 64
Pz <- generate.P.beta(n)
P <- Pz$P
z <- Pz$clustering
X <- embedding(P, 3, 1)
A <- draw.graph(P)
Xhat <- embedding(A, 3, 1)
A.graph <- tidygraph::as_tbl_graph(A, directed = FALSE)
